---
title: "YOUR TURN! UPDATE THIS TITLE."
author: "Your name"
output: html_document
params:
  species: Gentoo
---

### Your job: create a parameterized report using data from `penguins.csv`. 
- Your report should contain a ggplot graph of flipper length versus body mass for the **species** that you choose.

- In the `render_functions.R` script, create a function that will render the report for the species you pick, saved as an .html with format 'penguin_report_SPECIESNAME.html'. 

- In the `render_functions.R` script, write a for loop that will automatically render a separate report for *all species* in the data. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
penguins <- read_csv("penguins.csv")
library(tidyverse)
```

Making a function
```{r}
render_penguin_report = function(species) {
  rmarkdown::render(
    input = "your_turn.Rmd", # What's the input file to render?
    params = list(species = species), # What are the parameters?
    output_file = paste0(species, "_report", ".html") # What should I name the output file?
  )
}
```


Making a vector of species
```{r}

species <- unique(penguins$species)

ggplot(data = penguins, aes(x = body_mass_g, y = flipper_length_mm)) +
  geom_point()
```



Making a `for` loop
```{r}
for (species in species) {
  render_penguin_report(species)
}
```

